Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls

### 2019-12-09 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
Update SURV727_FinalPresentation_Padgett_Thiam.Rmd

## Pre-debate number of tweets 
```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate"}
props_tab1 %>%
  filter(Cat == "TRUE") %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
    labs(x = "Democratic Party Candidates", 
       y = "Number of Tweets", 
       caption = "Source: Twitter") 
```

## Post-debate number of tweets 
```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate"}
props_tab2 %>%
  filter(Cat == "TRUE") %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
    labs(x = "Democratic Party Candidates", 
       y = "Number of Tweets", 
       title = "Post Debate candidates mentions in Tweets", 
       caption = "Source: Twitter")

@@

 loc_pre_all %>%
  mutate(Location = loc) %>%
  group_by(Candidate, Location) %>%
  summarise(total = n()) %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -total), y=total, fill = Location)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       title = "Pre Debate candidates mentions in Tweets by location", 
       caption = "Source: Twiiter")

@@

 loc_post_all %>%
  mutate(Location = loc) %>%
  group_by(Candidate, Location) %>%
  summarise(total = n()) %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -total), y=total, fill = Location)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       title = "Post Debate candidates mentions in Tweets by location", 
       caption = "Source: Twiiter")

>>>>

## Pre-debate number of tweets 
```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate"}
props_tab1 %>%
  filter(Cat == "TRUE") %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
    labs(x = "Democratic Party Candidates", 
       y = "Number of Tweets", 
           caption = "Source: Twitter

                                 Figure 1") +
theme(axis.text.x=element_text(angle=90,hjust=1))

## Post-debate number of tweets 
```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate"}
props_tab2 %>%
  filter(Cat == "TRUE") %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
    labs(x = "Democratic Party Candidates", 
       y = "Number of Tweets", 
       title = "Post Debate candidates mentions in Tweets", 
            caption = "Source: Twitter

                                 Figure 2") +
theme(axis.text.x=element_text(angle=90,hjust=1))

@@

 loc_pre_all %>%
  mutate(Location = loc) %>%
  group_by(Candidate, Location) %>%
  summarise(total = n()) %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -total), y=total, fill = Location)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       title = "Pre Debate candidates mentions in Tweets by location", 
             caption = "Source: Twitter

                                 Figure 3") +
           theme(axis.text.x=element_text(angle=90,hjust=1))

@@

 loc_post_all %>%
  mutate(Location = loc) %>%
  group_by(Candidate, Location) %>%
  summarise(total = n()) %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -total), y=total, fill = Location)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       title = "Post Debate candidates mentions in Tweets by location", 
              caption = "Source: Twitter

                                 Figure 4") +
theme(axis.text.x=element_text(angle=90,hjust=1))
